---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
data = read_excel("../datasets/Data_Cortex_Nuclear.xls")
data
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```


```{r}
# Store operations in a variable with <- or =
ubiquitin_subset <-
  # Select the columns to keep, to select everything but a column use -
  data %>% select(MouseID, Ubiquitin_N, Genotype, ends_with("vior"), contains("Treat") , class) %>%
  # Keep rows of class c-CS-m and c-SC-m
  filter(class %in% c("c-CS-m","c-SC-m")) %>%
  # Sort increasing values by default, use desc(column_name) for descending
  arrange(Ubiquitin_N)

# Show the results
ubiquitin_subset

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
